IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/rebuttal.txt

We would like to thank all reviewers for their feedback and suggestions.
We will first reply to high-level comments and then reply to specific
questions in the reviews.

Reviewer 2 asks whether or not our method actually scales in practice,
pointing to our inability to deal with external effects as a mark
against it.  It is true that dealing with external effects is
important for pushing IFC into practice, and our work is not primarily
concerned with addressing this issue.  However, this problem is
endemic to all information flow control systems: for instance, JPMail [A]
re-implements primitives with external effects in Jif; Paragon [B]
internalizes external effects by wrapping the corresponding primitives
to be IFC-aware [C]; JSFlow [25,26] manually wraps JavaScript
primitives with external effects.  This is not to say that the systems
we have implemented do not deal with external effects: e.g.
XMLHttpRequest as used in COWL essential wraps the "native" unsafe
code. However, the treatment of external effects is very much
application specific, and finding a general solution is an open
problem.

@@

Thus, the generality of our system does not come from a treatment of
external effects; rather, assuming that external effects are taken
care of (Section 6), it comes from our ability to accommodate
arbitrarily complex internal semantics.  For example, our work is
directly applicable to "vanilla" JavaScript (ECMAScript), which does
not have any external effects.  As opposed to existing IFC systems
(e.g., [25]) which incur tremendous overhead, we show that you can
build an efficient, non-intrusive IFC system for JavaScript, or any
other language which can be isolated.

It's worth stating that we did not simply shoe-horn COWL and LIO into
a "unified framework".  While our language uses ideas from LIO and
COWL, we note that the current versions of these systems coevolved
with the concepts in the paper.  For instance, in LIO [53] (and Breeze
[28]) exceptions were originally treated in a rather complex fashion.
As we discuss in the paper, when you consider exceptions as part of
the internal semantics of the target language, the appropriate
semantics for exceptions fall out naturally in our framework.  In
fact, LIO was modified to adopt this new, simpler approach.

@@

Reviewer 1 was concerned that many aspects of our IFC system were
simply rehashes of prior work.  We believe that our core IFC
language's support for both concurrent and sequential scheduling
through asynchronous communication primitives is novel.  (Notice that
a primitive which may block cannot work in a sequential setting).
This is an old idea from IFC OS work, but formally reasoning about
this idea is new.

Reviewer 1 also asks whether or not the ideas in the extension section
were actually worked out.  The IFC language features and external
effect systems mentioned have been implemented for Haskell and
JavaScript, and, in the case of LIO, have had properties formally
proven, while the scheduling policies and type safety extensions are
more speculative.  The treatment of mutable references was explicitly
called out as unworkable: we would like to clarify an important
distinction between mutable references in the IFC language and mutable
references internally supported in the target language.  The naive
addition of IFC references results in two *different* types of
references: this is a feature, not a bug, since it absolves us of the
responsibility of integrating the two semantics.  Furthermore,
existing code using old references does not usually need to
communicate over IFC boundaries, so code being written to take
advantage of the new IFC support can be written to explicitly use IFC
references.  This approach of adding features to the core IFC calculus
extends to our other proposed extensions, and their security proofs
are generalizable to our setting in the same way.

Specific questions
------------------

As reviewer 3 points out, the reference about COWL does not include
an URL.  It is available at http://deian.net/swapi.pdf and currently
not indexed by search engines because the paper is being anonymously
submitted.  We apologize for the mistake.

@@

Reviewer 1 ask why we have not developed our formalism with a monad.
One of our motivations was to formalize an IFC system for JavaScript,
whose semantics are typically not presented in a stratified way by
distinguishing a monadic and a pure fragment.  A non-monadic approach
enables a more natural formalism for a large class of languages,
including JavaScript.

Reviewer 2 ask about the proof strategy for Theorem 3.  Performing
induction on the length of the derivation sequence followed by
induction on the derivation tree is standard for small-step
operational semantics.  This is isomorphic to induction on the
structure of the derivation for ->*.

Reviewer 3 asks about shared mutable references:  It is correct that a
different design choice might allow shared mutable references in this
way.  However, because native references are protected by the current
label, this would effectively be a fine-grained IFC system, requiring
checks for all reference reads and writes.  This would be against our
goal of a coarse-grained system.  We will improve the unfortunate
phrasing.

Reviewer 3 asks about the values sent across channels in COWL.  For
simplicity, we require them to be strings in the paper, thought any
structurally cloned object (as well as labeled blobs) are actually
permitted.

### 2014-07-08 paper/extensions.tex
s/SWAPI/COWL
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

While the IFC language presented thus far provides the basic
information flow primitives, actual IFC implementations
may wish to extend the minimal system with more specialized
constructs.
%Different concrete IFC implementations may wish to extend our minimal
%system with labeled constructs appropriate for their envisioned
%applications.
%%
For example, SWAPI provides a labeled version of the XHR object, while
LIO implements a labeled file system, used in server-side web
applications~\cite{hails}.
%%
%Below we
%consider the addition of several labeled constructs to the abstract specification.
In this section we show how to extend the language with several such
constructs.
%
%We remark that that the non-interference proofs must account for the
%new constructs, since they amend the IFC calculus semantics (usually
%by addition).

@@

Full details with formal reduction rules are provided
in \appendixext{}, but omitted here for space reasons.
%}

@@

\subsection{Clearance}
%
Systems like LIO, SWAPI, and Breeze additionally provide a discretionary access
control (DAC) mechanism---called \emph{clearance}---at the language
level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
%
This mechanisms is used to restrict a computation from allocating and
accessing data (or communicating with entities) above a specified
label, the clearance.
%
Amending our IFC language with clearance is straight forward,
and, can be done using our notation of a restricted language.
%
To this end, we first extend tasks to track a clearance label
alongside the current label, and amend the core IFC language with two
new terminals for retrieving and setting this value.
%
Since this extension only adds a per-task mutable variable whose value
has no influence on the system, all security guarantees still
hold, by essentially the same proofs.
%
However, this does not implement any DAC mechanism yet.
%
To do so, we can restrict the language with a family of predicates
$\mathcal{P}_\text{clearance}$:
All rules that
raise the current label (e.g., \textsc{I-setLabel}), perform
allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}), or set the
clearance (clearance should not be arbitrarily raised), a predicate
that uses the clearance to impose DAC is used.
%
For instance, the predicate for \textsc{I-setLabel} prevents the
current label from being raised above the clearance (and thus permit
reads above the clearance).  The predicate $P := |il
canFlowTo il'|$ achieves this restriction, where |il'| is the
clearance and |il| is the current
label.
%
The other predicates are defined in a similar way and omitted for
brevity.

@@

\subsection{Privileges}
Decentralized IFC extends IFC with the decentralized label model of
Myers and Liskov~\cite{myers:dlm} to allow for more general
applications, including systems consisting of mutually distrustful
parties.  In a decentralized system, a computation is executed with a
set of \emph{privileges}, which, when exercised, allow the computation
to declassify data (e.g., by lowering the current label).
%
Practical IFC systems
(e.g.,~\cite{Zeldovich:2006, lio,
  Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
implement many applications.
%
%Since both the LIO and SWAPI implementations already support such features,
%we believe that extending our calculus to consider privileges is
%straight forward.
%
The challenge with such an extension lies in the precise
security guarantees that must be proved, which to the best of our
knowledge is an open research problem.

Our implementation for Node.js and SWAPI both provide privileges, but
we have not formalized this part any further.
%
%Addressing this problem is a natural direction for this work.

@@

Like labeled references, features with external effects must be
modeled in the IFC language; we must reason about the precise security
implications of features that otherwise inherently leak data.
%
Previous approaches have modeled external effects by internalizing the
effects as writes/reads to labeled channels/references~\cite{stefan:addressing-covert}.
%
An alternative approach is to model such effects as messages to/from
certain labeled tasks.
%
These ``special'' tasks are trusted with access to the unlabeled
primitives that can be used to perform the external effects; since the
interface to these tasks is already part of the IFC language, the
proof only requires showing that this task does not leak information.
%
This latter approach of wrapping unsafe primitives is, for example,
used in SWAPI to allow for controlled network communication.
%
By wrapping the default XHR object, for example, we can allow code
to communicate with hosts according to the task's current label.

>>>>

While the IFC language presented thus far provides the basic
information flow primitives, actual IFC implementations
may wish to extend the minimal system with more specialized
constructs.
%Different concrete IFC implementations may wish to extend our minimal
%system with labeled constructs appropriate for their envisioned
%applications.
%%
For example, COWL provides a labeled version of the XHR object, while
LIO implements a labeled file system, used in server-side web
applications~\cite{hails}.
%%
%Below we
%consider the addition of several labeled constructs to the abstract specification.
In this section we show how to extend the language with several such
constructs.
%
%We remark that that the non-interference proofs must account for the
%new constructs, since they amend the IFC calculus semantics (usually
%by addition).

@@

Full details with formal reduction rules are provided
in \appendixextfirst{}, but omitted here for space reasons.
%}

@@

\subsection{Clearance}
%
Systems like LIO, COWL, and Breeze additionally provide a discretionary access
control (DAC) mechanism---called \emph{clearance}---at the language
level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
%
This mechanisms is used to restrict a computation from allocating and
accessing data (or communicating with entities) above a specified
label, the clearance.
%
Amending our IFC language with clearance is straight forward,
and, can be done using our notation of a restricted language.
%
To this end, we first extend tasks to track a clearance label
alongside the current label, and amend the core IFC language with two
new terminals for retrieving and setting this value.
%
Since this extension only adds a per-task mutable variable whose value
has no influence on the system, all security guarantees still
hold, by essentially the same proofs.
%
However, this does not implement any DAC mechanism yet.
%
To do so, we can restrict the language with a family of predicates
$\mathcal{P}_\text{clearance}$:
All rules that
raise the current label (e.g., \textsc{I-setLabel}), perform
allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}), or set the
clearance (clearance should not be arbitrarily raised), a predicate
that uses the clearance to impose DAC is used.
%
For instance, the predicate for \textsc{I-setLabel} prevents the
current label from being raised above the clearance (and thus permit
reads above the clearance).  The predicate $P := |il
canFlowTo il'|$ achieves this restriction, where |il'| is the
clearance and |il| is the current
label.
%
The other predicates are defined in a similar way and omitted for
brevity.

@@

\subsection{Privileges}
Decentralized IFC extends IFC with the decentralized label model of
Myers and Liskov~\cite{myers:dlm} to allow for more general
applications, including systems consisting of mutually distrustful
parties.  In a decentralized system, a computation is executed with a
set of \emph{privileges}, which, when exercised, allow the computation
to declassify data (e.g., by lowering the current label).
%
Practical IFC systems
(e.g.,~\cite{Zeldovich:2006, lio,
  Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
implement many applications.
%
%Since both the LIO and COWL implementations already support such features,
%we believe that extending our calculus to consider privileges is
%straight forward.
%
The challenge with such an extension lies in the precise
security guarantees that must be proved, which to the best of our
knowledge is an open research problem.

Our implementation for Node.js and COWL both provide privileges, but
we have not formalized this part any further.
%
%Addressing this problem is a natural direction for this work.

@@

Like labeled references, features with external effects must be
modeled in the IFC language; we must reason about the precise security
implications of features that otherwise inherently leak data.
%
Previous approaches have modeled external effects by internalizing the
effects as writes/reads to labeled channels/references~\cite{stefan:addressing-covert}.
%
An alternative approach is to model such effects as messages to/from
certain labeled tasks.
%
These ``special'' tasks are trusted with access to the unlabeled
primitives that can be used to perform the external effects; since the
interface to these tasks is already part of the IFC language, the
proof only requires showing that this task does not leak information.
%
This latter approach of wrapping unsafe primitives is, for example,
used in COWL to allow for controlled network communication.
%
By wrapping the default XHR object, for example, we can allow code
to communicate with hosts according to the task's current label.

### 2014-07-08 paper/jcm.tex
s/SWAPI/COWL
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Our overall plan will be to take a \textbf{{\color{red} target
language}} with a formal operational semantics and combine it with an
\textit{{\color{blue} information flow control language}}.  For example,
taking ECMAScript as the target language and combining it with our IFC
language should produce the formal semantics for SWAPI.  In this
presentation, we use a simple, untyped lambda calculus with mutable
references and fixpoint in place of ECMAScript, to demonstrate some of the key
properties without having too much detail; we discuss the proper
embedding in more detail in Section~\ref{sec:real}.

@@

In the introduction, we stated that the original motivation behind
developing this embedding was in order to formally specify a
coarse-grained information flow control language for JavaScript.
%
In Section~\ref{sec:retrofit}, however, we used only a simplified
language as an example target language.
%
In this section, we consider the application of our embedding to
JavaScript and two other real world target languages, C and Haskell.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different features and properties, as well as discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
Two of the systems we describe have been implemented: the Haskell
system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
implementation of the IFC system for C to future work.

@@

We describe SWAPI~\cite{swapi}, an implementation of this system for JavaScript
(which we here denote by \ensuremath{\Red{\lambda_{\text{JS}}}}).
%
The direct approach for implementing the embedded language \ensuremath{L_\text{IFC}(\textsc{RR},\Red{\lambda_{\text{JS}}})} is
by running multiple instances of the JS runtime, i.e., in
separate OS-level threads.\footnote{
 The Firefox implementation of SWAPI also considers the case where
 tasks share the JavaScript runtime (and are cooperatively scheduled
 on the event-loop), but the heap and execution context of each task
 is disjoint. This is similar to the single-heap language of
 Section~\ref{sec:concrete}.  However, since the heap separation is
 provided by the browser the browser, we do not discuss this further.
 The interested reader is referred to~\cite{swapi} for more details.
}
%
In SWAPI, the IFC language functionality is implemented in the JS
runtime much like browser layout engines implement the DOM, and expose
the new functions, e.g., \text{\tt getElementById}, by attaching them to
the global JS object.
%
In turn, each task created with \ensuremath{\mathbf{sandbox}} is
executed in a separate thread, running a separate, \emph{fresh} instance of our
modified JS runtime.
%
Formally, \ensuremath{\mathbf{sandbox}} is defined with \ensuremath{\kappa\;(\tar{\Sigma})\mathrel{=}\tar{\Sigma}_{0}}, where \ensuremath{\tar{\Sigma}_{0}} is the global object corresponding to the standard
JS library (e.g., \ensuremath{\tar{\Sigma}_{0}} contains \texttt{Object}, \texttt{Array},
etc.).

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains references.
%
As discussed in Section~\ref{sec:concrete}, we need to restrict \ensuremath{\mathbf{send}}
to expressions that can be marshalled as strings, i.e., structurally
clonable objects.
%
In our formalization, this amounts to restricting the IFC language rule
for \ensuremath{\mathbf{send}} such that only strings can be shared:
\newcommand{\str}{"string"}
\begin{mathpar}
\inferrule[JS-send]
{
\ensuremath{\ifc{l}\;\flows{}\;\ifc{l}'}\\
\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}}')\mathrel{=}\ifc{\Theta}}\\
\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\;[\mskip1.5mu \ifc{\Varid{i}}'\mapsto{}(\ifc{l}',\ifc{\Varid{i}},\ifc{\Varid{v}}),\ifc{\Theta}\mskip1.5mu]}\\
\ensuremath{\ifc{\Varid{e}}\mathrel{=}\ifc{^{\textrm{IT}}\lceil}\tar{e}\ifc{\rceil}}\\
\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\texttt{typeOf}(\tar{e})\texttt{ === \str}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\texttt{true}\right]}
}
{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{l}'\;\ifc{\Varid{v}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots\hookrightarrow\ifc{\Sigma}';\alpha_{{\tiny\mathrm{\Sigma}}}(\langle \tar{\Sigma}, \ifc{E}\ifc{[}\langle\rangle\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots)}}
\end{mathpar}
We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and worker
communications~\cite{webworkers}.
%
Thus, the SWAPI implementation provides an IFC version of
\texttt{postMessage}, defined in terms of \ensuremath{\mathbf{send}}, that additionally
takes a label argument.

Unsurprisingly, our coarse-grained combined language approach has been
inspired by existing browser (security) architectures.
%
Browsers, for example, isolate pages of different origins by running
them in separate runtimes.
%
Similarly, they provide the worker JS object~\cite{webworkers}, which allows
JavaScript to execute code in separate threads with separate JS
runtimes (and fresh global objects).
%
In both cases, code relies on the \texttt{postMessage} message-passing
API for communication, similar to our system.\footnote{
  The message-passing approach is, in part, due to ECMAScript's lack
  of well-defined semantics for concurrency.
  %
  Hence sharing and accessing objects such as the DOM across worker
  threads is undefined.
}
%
As suggested by our formal semantics, SWAPI can directly leverage these
mechanisms to implement the semantics of \ensuremath{L_\text{IFC}(\textsc{RR},\Red{\lambda_{\text{JS}}})}
without modifying the JS runtime or intrusively changing the browser
layout engine.

However, a simple implementation of just associating a label with
workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient, as APIs which
introduce extra computational effects must be manually made aware of information flow
control.
%
For example, the initial global object of a worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM.
%
In both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%
To address this, SWAPI additionally uses content security policy (CSP) and
(iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
to the label of a task (worker or browsing context).  Accomodating these
features lies outside the purview of our formalism.

%% \Red{
%% EZY:  This seems like useless detail about the SWAPI implementation
%% that is not relevant to this paper.
%% 
%% Of course, simply disallowing all external effects for all browsing
%% contexts would break most of the Web.
%% %
%% Hence SWAPI only enforces IFC, and thus restricts external effects,
%% when the JS code uses the new API.\footnote{
%%   Once a piece of code ``opts-in'' to use our IFC API, in addition to
%%   restricting external effects we interpose ``standard''
%%   \texttt{postMessage} communication to ensure that no information is
%%   leaked between contexts that have opted-in and those that have not.
%% }
%% %
%% Moreover, rather than disallowing all external effects, SWAPI allows
%% controlled network communication by leveraging the fact that web
%% pages already have an accompanying security policy: the same origin
%% policy.
%% %
%% Hence, for example, a worker that has read data only sensitive to
%% \texttt{http://bank.ch} can communicate with this domain; only once
%% \texttt{http://aws.com} data is also included in the context will all
%% network requests be blocked.
%% %
%% Of course, this requires that we use a concrete label format to
%% express the policies; we refer the interested reader to~\tocite{} for
%% more details.}
\section{Extensions and Limitations}
\label{sec:extensions}

@@

Different concrete IFC implementations may wish to extend our minimal
system with labeled constructs appropriate for their envisioned
applications.
%
For example, SWAPI provides a labeled version of the XHR object, while
LIO implements a labeled file system, use in server-side web
applications~\cite{hails}.
%
Below we
consider the addition of several labeled constructs to the abstract specification.
%
We remark that that the non-interference proofs must account for the
new constructs, since they amend the IFC calculus semantics (usually
by addition).

@@

\paragraph{Privileges}
Decentralized IFC extends IFC with the decentralized label model of
Myers and Liskov~\cite{myers:dlm} to allow for more general
applications, including systems consisting of mutually distrustful
parties.  In a decentralized system, a computation is executed with a
set of \emph{privileges}, which, when exercised, allow the computation
to declassify data (e.g., by lowering the current label).
%
Practical IFC systems
(e.g.,~\cite{Zeldovich:2006, lio,
Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
implement many applications.
%
Since both the LIO and SWAPI implementations already support such features,
we believe that extending our calculus to consider privileges is
straight forward.
%
However, the challenge with such an extension lies in the precise
security guarantees that must be proved.
%
%Addressing this problem is a natural direction for this work.

\paragraph{Clearance}
%
LIO, SWAPI, and Breeze additionally provide a discretionary access
control mechanism---called \emph{clearance}---at the language
level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}; this mechanisms is
used to restrict a computation from accessing data (or communicating
with entities) above a specified label, the clearance.
%
For simplicity, we omitted clearance from our formalism.
%
We only remark that the mechanism generalizes beyond these IFC systems
in a straight forward manner and does not affect our definitions or
proofs in any meaningful way.

@@

Like labeled references, features with external effects must be
modeled in the IFC language; we must reason about the precise security
implications of features that otherwise inherently leak data.
%
Previous approaches have modeled external effects by internalizing the
effects as writes/reads to labeled channels/references~\tocite{}.
%
An alternative approach is to model such effects as messages to/from
certain labeled tasks.
%
These ``special'' tasks are trusted with access to the unlabeled
primitives that can be used to perform the external effects; since the
interface to these tasks is already part of the IFC language, the
proof only requires showing that this task does not leak information.
%
This latter approach of wrapping unsafe primitives is, for example,
used in SWAPI to allow for controlled network communication.
%
By wrapping the default XHR object, for example, we can allow code
to communicate with hosts according to the task's current label.
\section{Proofs}
\label{sec:proofs}

>>>>

Our overall plan will be to take a \textbf{{\color{red} target
language}} with a formal operational semantics and combine it with an
\textit{{\color{blue} information flow control language}}.  For example,
taking ECMAScript as the target language and combining it with our IFC
language should produce the formal semantics for COWL.  In this
presentation, we use a simple, untyped lambda calculus with mutable
references and fixpoint in place of ECMAScript, to demonstrate some of the key
properties without having too much detail; we discuss the proper
embedding in more detail in Section~\ref{sec:real}.

@@

In the introduction, we stated that the original motivation behind
developing this embedding was in order to formally specify a
coarse-grained information flow control language for JavaScript.
%
In Section~\ref{sec:retrofit}, however, we used only a simplified
language as an example target language.
%
In this section, we consider the application of our embedding to
JavaScript and two other real world target languages, C and Haskell.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different features and properties, as well as discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
Two of the systems we describe have been implemented: the Haskell
system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
implementation of the IFC system for C to future work.

@@

We describe COWL~\cite{swapi}, an implementation of this system for JavaScript
(which we here denote by \ensuremath{\Red{\lambda_{\text{JS}}}}).
%
The direct approach for implementing the embedded language \ensuremath{L_\text{IFC}(\textsc{RR},\Red{\lambda_{\text{JS}}})} is
by running multiple instances of the JS runtime, i.e., in
separate OS-level threads.\footnote{
 The Firefox implementation of COWL also considers the case where
 tasks share the JavaScript runtime (and are cooperatively scheduled
 on the event-loop), but the heap and execution context of each task
 is disjoint. This is similar to the single-heap language of
 Section~\ref{sec:concrete}.  However, since the heap separation is
 provided by the browser the browser, we do not discuss this further.
 The interested reader is referred to~\cite{swapi} for more details.
}
%
In COWL, the IFC language functionality is implemented in the JS
runtime much like browser layout engines implement the DOM, and expose
the new functions, e.g., \text{\tt getElementById}, by attaching them to
the global JS object.
%
In turn, each task created with \ensuremath{\mathbf{sandbox}} is
executed in a separate thread, running a separate, \emph{fresh} instance of our
modified JS runtime.
%
Formally, \ensuremath{\mathbf{sandbox}} is defined with \ensuremath{\kappa\;(\tar{\Sigma})\mathrel{=}\tar{\Sigma}_{0}}, where \ensuremath{\tar{\Sigma}_{0}} is the global object corresponding to the standard
JS library (e.g., \ensuremath{\tar{\Sigma}_{0}} contains \texttt{Object}, \texttt{Array},
etc.).

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains references.
%
As discussed in Section~\ref{sec:concrete}, we need to restrict \ensuremath{\mathbf{send}}
to expressions that can be marshalled as strings, i.e., structurally
clonable objects.
%
In our formalization, this amounts to restricting the IFC language rule
for \ensuremath{\mathbf{send}} such that only strings can be shared:
\newcommand{\str}{"string"}
\begin{mathpar}
\inferrule[JS-send]
{
\ensuremath{\ifc{l}\;\flows{}\;\ifc{l}'}\\
\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}}')\mathrel{=}\ifc{\Theta}}\\
\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\;[\mskip1.5mu \ifc{\Varid{i}}'\mapsto{}(\ifc{l}',\ifc{\Varid{i}},\ifc{\Varid{v}}),\ifc{\Theta}\mskip1.5mu]}\\
\ensuremath{\ifc{\Varid{e}}\mathrel{=}\ifc{^{\textrm{IT}}\lceil}\tar{e}\ifc{\rceil}}\\
\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\texttt{typeOf}(\tar{e})\texttt{ === \str}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\texttt{true}\right]}
}
{\ensuremath{\ifc{\Sigma};\langle \tar{\Sigma}, \ifc{E}\ifc{[}\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{l}'\;\ifc{\Varid{v}}\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots\hookrightarrow\ifc{\Sigma}';\alpha_{{\tiny\mathrm{\Sigma}}}(\langle \tar{\Sigma}, \ifc{E}\ifc{[}\langle\rangle\ifc{]}_\ifc{I}\rangle^{\ifc{\Varid{i}}}_{\ifc{l}},\ldots)}}
\end{mathpar}
We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and worker
communications~\cite{webworkers}.
%
Thus, the COWL implementation provides an IFC version of
\texttt{postMessage}, defined in terms of \ensuremath{\mathbf{send}}, that additionally
takes a label argument.

Unsurprisingly, our coarse-grained combined language approach has been
inspired by existing browser (security) architectures.
%
Browsers, for example, isolate pages of different origins by running
them in separate runtimes.
%
Similarly, they provide the worker JS object~\cite{webworkers}, which allows
JavaScript to execute code in separate threads with separate JS
runtimes (and fresh global objects).
%
In both cases, code relies on the \texttt{postMessage} message-passing
API for communication, similar to our system.\footnote{
  The message-passing approach is, in part, due to ECMAScript's lack
  of well-defined semantics for concurrency.
  %
  Hence sharing and accessing objects such as the DOM across worker
  threads is undefined.
}
%
As suggested by our formal semantics, COWL can directly leverage these
mechanisms to implement the semantics of \ensuremath{L_\text{IFC}(\textsc{RR},\Red{\lambda_{\text{JS}}})}
without modifying the JS runtime or intrusively changing the browser
layout engine.

However, a simple implementation of just associating a label with
workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient, as APIs which
introduce extra computational effects must be manually made aware of information flow
control.
%
For example, the initial global object of a worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM.
%
In both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%
To address this, COWL additionally uses content security policy (CSP) and
(iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
to the label of a task (worker or browsing context).  Accomodating these
features lies outside the purview of our formalism.

%% \Red{
%% EZY:  This seems like useless detail about the COWL implementation
%% that is not relevant to this paper.
%% 
%% Of course, simply disallowing all external effects for all browsing
%% contexts would break most of the Web.
%% %
%% Hence COWL only enforces IFC, and thus restricts external effects,
%% when the JS code uses the new API.\footnote{
%%   Once a piece of code ``opts-in'' to use our IFC API, in addition to
%%   restricting external effects we interpose ``standard''
%%   \texttt{postMessage} communication to ensure that no information is
%%   leaked between contexts that have opted-in and those that have not.
%% }
%% %
%% Moreover, rather than disallowing all external effects, COWL allows
%% controlled network communication by leveraging the fact that web
%% pages already have an accompanying security policy: the same origin
%% policy.
%% %
%% Hence, for example, a worker that has read data only sensitive to
%% \texttt{http://bank.ch} can communicate with this domain; only once
%% \texttt{http://aws.com} data is also included in the context will all
%% network requests be blocked.
%% %
%% Of course, this requires that we use a concrete label format to
%% express the policies; we refer the interested reader to~\tocite{} for
%% more details.}
\section{Extensions and Limitations}
\label{sec:extensions}

@@

Different concrete IFC implementations may wish to extend our minimal
system with labeled constructs appropriate for their envisioned
applications.
%
For example, COWL provides a labeled version of the XHR object, while
LIO implements a labeled file system, use in server-side web
applications~\cite{hails}.
%
Below we
consider the addition of several labeled constructs to the abstract specification.
%
We remark that that the non-interference proofs must account for the
new constructs, since they amend the IFC calculus semantics (usually
by addition).

@@

\paragraph{Privileges}
Decentralized IFC extends IFC with the decentralized label model of
Myers and Liskov~\cite{myers:dlm} to allow for more general
applications, including systems consisting of mutually distrustful
parties.  In a decentralized system, a computation is executed with a
set of \emph{privileges}, which, when exercised, allow the computation
to declassify data (e.g., by lowering the current label).
%
Practical IFC systems
(e.g.,~\cite{Zeldovich:2006, lio,
Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
implement many applications.
%
Since both the LIO and COWL implementations already support such features,
we believe that extending our calculus to consider privileges is
straight forward.
%
However, the challenge with such an extension lies in the precise
security guarantees that must be proved.
%
%Addressing this problem is a natural direction for this work.

\paragraph{Clearance}
%
LIO, COWL, and Breeze additionally provide a discretionary access
control mechanism---called \emph{clearance}---at the language
level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}; this mechanisms is
used to restrict a computation from accessing data (or communicating
with entities) above a specified label, the clearance.
%
For simplicity, we omitted clearance from our formalism.
%
We only remark that the mechanism generalizes beyond these IFC systems
in a straight forward manner and does not affect our definitions or
proofs in any meaningful way.

@@

Like labeled references, features with external effects must be
modeled in the IFC language; we must reason about the precise security
implications of features that otherwise inherently leak data.
%
Previous approaches have modeled external effects by internalizing the
effects as writes/reads to labeled channels/references~\tocite{}.
%
An alternative approach is to model such effects as messages to/from
certain labeled tasks.
%
These ``special'' tasks are trusted with access to the unlabeled
primitives that can be used to perform the external effects; since the
interface to these tasks is already part of the IFC language, the
proof only requires showing that this task does not leak information.
%
This latter approach of wrapping unsafe primitives is, for example,
used in COWL to allow for controlled network communication.
%
By wrapping the default XHR object, for example, we can allow code
to communicate with hosts according to the task's current label.
\section{Proofs}
\label{sec:proofs}
